Motor Trend Analysis of MPG covariates between Manual and Automatic Transmission Cars (think of a better title)
=====================================================================================
```{r,echo=FALSE}
library(datasets)
data(mtcars)
```

## Executive Summary

[Broadest conclusion (yes there is an association between transmision type and MPG); sumary of breakdown by features that impact this relationship. - 1 Paragraph]

## Exploration

Before embarking on our deeper analysis and drawing conclusions from our data, we can start with some exploration to gain some basic understanding of the MPG covariates and glean hints of some of the relationships that may exist in the data.

### Starting from the beginning: Looking at MPG and transmission type

Since our questions of interest relate to potential differences in cars' MPG by car transmission type (automatic or manual), we start with these two variables.  Plotting MPG against transmission type and fitting a linear model shows a significant difference between the slope and zero, as seen in the R output below.  This is equivalent to testing the hypothesis that the means of MPG between the transmission types are significantly different from one another, which is clear in **Figure 1** in the Appendix.  The slope here is interpreted as the increase in expected MPG, going from an automatic transmission (am=0 in the dataset) to a manual transmission (am=1 in the dataset).  

```{r, echo=FALSE}
lmobvious <- lm(mpg~am, data=mtcars)
summary(lmobvious)$coefficients
```

So we can see that we would expect to see about a 7 MPG fuel efficiency increase, on average, moving from an automatic to manual transmission.  Now that we know this, we can try to dig deeper into the data and find out more specifically what is driving this effect.

### Digging deeper

To help us try to find what covariates might have the most significant impact on the relationship between transmission type and MPG, we can look at a pairs plot of all of the data we have available, keeping an eye out for two things: what variables have a noticeable relationship to MPG, and in which cases is that relationship informed by transmission type?  The pairs plot can be seen in **Figure 2** in the Appendix.

While harder to discern in the smaller report output, the pairwise plots against MPG for displacement (engine size), rear axle ratio, quarter mile time, number of forward gears, number of carburetors, and possibly number of cylinders appear to show the type of relationship we are interested in: related to MPG, but with a clear separation in the data as they relate to MPG by transmission type. 

Before going in to our model building, we may already be able to tell that some of these features are less interesting than others.  For example, a car's quarter mile time is likely to be highly correlated with things like engine size and number of cylinders, and possibly several of the others -- even for someone who knows less about the inner workings of cars and prefers to admire them for their styling, it is logical that quarter mile time would be more of an effect in the data than a cause.  There may be other relationships between these particular variables that have similar information overlaps and may not be necessary to include in a parsimonious model.

## Model Selection

There are two broad approaches we could take to building models, based on our exploration so far.  The first approach involves focusing on the variables which most significantly affect MPG in a multivariate analysis and then modeling the interaction of transmission type with those variables to see its effect on MPG through them.  The second approach would be to focus on the non-MPG variables that have the most significant interaction with the transmission variable, and then model based on those.  We will use the first approach to keep our focus on the outcome of interest (MPG), with the understanding that the second may provide additional insights if performed as well.

### Building our models: variable winnowing



based on exploration, we can "guess" at the order in which variables might have importance; we can build some "adjusted" and "unadjusted" models here

***Think about how interactions work here... is "am" a dummy variable? seems like it should be.

### Model selection with interactions

<using ANOVA or similar method based on prior section ? >

clearly denote "final model"

## Analysis and Conclusions

interpret the coefficients of the final multivariate model correctly; reiterate the answer to the 2 questions of interest; quantify the uncertainty in conclusions <how to do this? CI?>

## Ex-post Diagnostics

residual plot, other diagnostics - think about this

## [make sure not missing anything else from grading rubric!] - put github repo link here maybe, or at top of appendix

## Appendix: Graphical Figures

#### Figure 1
```{r, echo=FALSE}
plot(mtcars$am, mtcars$mpg, pch=19, col=ifelse(mtcars$am==1, "salmon", "steelblue"), xlab="Transmission Type", ylab="Miles per Gallon", main="MPG by Transmission Type")
legend("topleft", fill=c("steelblue", "salmon"), legend=c("Automatic", "Manual"))
lmobvious <- lm(mpg~am, data=mtcars)
abline(lmobvious, lwd=2)
```

#### Figure 2
```{r, echo=FALSE}
pairs(mtcars[,-9], panel=panel.smooth, col=ifelse(mtcars$am==1, "salmon", "steelblue"), pch=19)
```

#### Figure 3

