Scratch work / exploratory graphs / rough conclusions re: Motor Trend MPG data analysis
===================================
```{r}
library(datasets)
data(mtcars)
```

## things to go here

```{r}
#qplot(mtcars$disp, mtcars$mpg, color=mtcars$am)
plot(mtcars$disp, mtcars$mpg, col=ifelse(mtcars$am==1, "salmon", "steelblue"), pch=19)
```

looks like different slopes for auto and manual wrt displacement

```{r}
plot(mtcars$cyl, mtcars$mpg, col=ifelse(mtcars$am==1, "salmon", "steelblue"), pch=19)
abline(lm(mpg~cyl, data=subset(mtcars, mtcars$am==1)))
abline(lm(mpg~cyl, data=subset(mtcars, mtcars$am==0)))
```

this plots mpg by cylinder with individual regression lines for each transmission type; looks different

```{r}
lmtest <- lm(mpg~am*cyl + am*disp + am*hp + am*drat + am*wt + am*qsec + am*vs + am*gear + am*carb, data=mtcars)
summary(lmtest)
```

examine this in greater detail - fits interaction of am with everything else -- not sure if this is theoretically valid, but may reveal some relationships (?)

```{r}
pairs(mtcars[,-9], panel=panel.smooth, col=ifelse(mtcars$am==1, "salmon", "steelblue"), pch=19)
```

Again, not entirely sure what I am looking for here; need to clear my head on this

### START WITH THE BASICS:
```{r}
plot(mtcars$am, mtcars$mpg, pch=19, col=ifelse(mtcars$am==1, "salmon", "steelblue"), xlab="Transmission Type", ylab="Miles per Gallon", main="MPG by Transmission Type")
legend("topleft", fill=c("steelblue", "salmon"), legend=c("Automatic", "Manual"))
lmobvious <- lm(mpg~am, data=mtcars)
abline(lmobvious, lwd=2)
```

Analysis: the basic model provides a basic answer, there is a clearly significant effect.  However, we probably care not so much that there is a general effect, but what OTHER variables relate to this.  Work from this as the starting point, then get fancier with the multivariate regression analysis using something like ANOVA to determine a reasonable model that accounts for other features of the data without "overfitting", essentially.  OCCAM's RAZOR.

