Scratch work / exploratory graphs / rough conclusions re: Motor Trend MPG data analysis
===================================
```{r}
library(datasets)
data(mtcars)
```

## things to go here

```{r}
#qplot(mtcars$disp, mtcars$mpg, color=mtcars$am)
plot(mtcars$disp, mtcars$mpg, col=ifelse(mtcars$am==1, "salmon", "steelblue"), pch=19)
```

looks like different slopes for auto and manual wrt displacement

```{r}
plot(mtcars$cyl, mtcars$mpg, col=ifelse(mtcars$am==1, "salmon", "steelblue"), pch=19)
abline(lm(mpg~cyl, data=subset(mtcars, mtcars$am==1)))
abline(lm(mpg~cyl, data=subset(mtcars, mtcars$am==0)))
```

this plots mpg by cylinder with individual regression lines for each transmission type; looks different

```{r}
lmtest <- lm(mpg~am*cyl + am*disp + am*hp + am*drat + am*wt + am*qsec + am*vs + am*gear + am*carb, data=mtcars)
summary(lmtest)
```

examine this in greater detail - fits interaction of am with everything else -- not sure if this is theoretically valid, but may reveal some relationships (?)

```{r}
pairs(mtcars[,-9], panel=panel.smooth, col=ifelse(mtcars$am==1, "salmon", "steelblue"), pch=19)
```

Again, not entirely sure what I am looking for here; need to clear my head on this

### START WITH THE BASICS:
```{r}
plot(mtcars$am, mtcars$mpg, pch=19, col=ifelse(mtcars$am==1, "salmon", "steelblue"), xlab="Transmission Type", ylab="Miles per Gallon", main="MPG by Transmission Type")
legend("topleft", fill=c("steelblue", "salmon"), legend=c("Automatic", "Manual"))
lmobvious <- lm(mpg~am, data=mtcars)
abline(lmobvious, lwd=2)
```

Analysis: the basic model provides a basic answer, there is a clearly significant effect.  However, we probably care not so much that there is a general effect, but what OTHER variables relate to this.  Work from this as the starting point, then get fancier with the multivariate regression analysis using something like ANOVA to determine a reasonable model that accounts for other features of the data without "overfitting", essentially.  OCCAM's RAZOR.


summary(lm(mpg~disp*am + carb*am, data=testcopy))

for interaction, the Intercept is auto intcpt, intercept + am1 is manual intctp, disp is auto displ slope, disp + disp:am1 is manual disp slope; etc. for the third

basically i think the "approach" might be a combination of winnowing a few factors with ANOVA without considering the interaction, since the terms that we're winnowing have already been "explored" to have the kind of relationship we're looking for.  Then once winnowed to the top 2-3, do the interaction on those and interpret the coefficients. 
MAIN THING NEEDED HERE IF THIS APPROACH IS USED: proper ANOVA, and proper interpretation of P-values for interacted terms.

Counter-argument: starting the wrong way; don't trust visual exploration / quick lms -- more robustly look at individual interactions and see which are ACTUALLY significant, not just "close" or "look like they might be", and then build up a model from there on that basis using ANOVA.  

Not sure which is the right approach here; maybe just do the first one since I've already started, and in "conclusions" or whatever note the other way to do it; but BOTTOM LINE is keep the question in mind and make sure it has been answered -- there may be another answer that some one else thinks is more "analytically correct", but does MY answer also provide something useful?  this is important to remember

the options in brief are, see which covariates that appear meaningful to MPG wash out in ANOVA and then look at the interaction on those covariates, or see which covariates appear to have a meaningful am dimension to them and then see which wash out in ANOVA from that group.

Argument for option 1: focuses on the things which most significantly affect mpg, which is the "outcome" we care about
Argument for option 2: focuses on the things that am most significantly affects, which is the "variable" we care about

```{r}
#base set from exploration
lmex <- lm(mpg~cyl + disp + drat + qsec + gear + carb, data=mtcars)
#winnow 1
lmex2 <- lm(mpg~carb + disp + gear + drat, data=mtcars)
#winnow 2
lmex3 <- lm(mpg~carb + disp + gear, data=mtcars)
## everything now significant
```

```{r}
#reconfirm with ANOVA
testfit1 <- lm(mpg~carb + disp + gear, data=mtcars)
testfit2 <- lm(mpg~carb + disp + gear + drat, data=mtcars)
testfit3 <- lm(mpg~carb + disp + gear + drat + qsec, data=mtcars)
anova(testfit1, testfit2, testfit3)
```
